Quantifying the manageability of pollination networks in an invasion context

### 2017-02-28 paper/draft_2.Rmd
Add extra reference to Ruths in the methods

Given the respective dependences, the extent to which a species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa). 
We therefore simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
This simplification, while maintaining ecological realism, is advantageous for several reasons. 
First, it is consistent with previous advances in structural controllability; second, it avoids complications related to the introduction of artificial control cycles; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
Furthermore, we show that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative *n~D~* of different networks (Table S3).

>>>>

Given the respective dependences, the extent to which a species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa). 
We therefore simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
This simplification, while maintaining ecological realism, is advantageous for several reasons. 
First, it is consistent with previous advances in structural controllability; second, it avoids complications related to the introduction of artificial control cycles [@Ruths2014]; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
Furthermore, we show that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative *n~D~* of different networks (Table S3).
